Statistical Modeling of Galaxy Catalogues with Normalizing Flows

### 2023-01-06 src/tex/ms.tex
Fixed dirac affil.
Moving figures.
Removed Francois as author

\author[0000-0001-5576-8189]{Andrew~J.~Connolly}
\affiliation{DIRAC Institute and the Department of Astronomy, University of Washington, Seattle, WA 98195, USA}

\author{François~Lanusse}

\author{Alex~I.~Malz}

@@

@@

\begin{figure*}[t]
    \script{photo-z/plot_ensemble_posteriors.py}
    \begin{centering}
        \includegraphics{figures/ensemble_posteriors.pdf}
        \caption{
            The ensemble of posteriors for three example galaxies.
            Flows 1-4 label the individual posteriors produced by each of the flows that make up the ensemble.
            The dashed black line is the mean of these individual posteriors and is the value used by the ensemble.
            The vertical gray line labeled ``Truth'' denotes the true redshift of the galaxy.
            Note these galaxies were specifically chosen for their broad, multimodal posteriors.
            The posteriors of most galaxies are sharp and unimodal.
        }
        \label{fig:ensemble-posteriors}
    \end{centering}
\end{figure*}

@@

\begin{acknowledgements}
    J.~F.~Crenshaw, B.~J.~Kalmbach, and A.~J.~Connolly acknowledge support from the DiRAC Institute in the Department of Astronomy at the University of Washington.
    The DIRAC Institute is supported through generous gifts from the Charles and Lisa Simonyi Fund for Arts and Sciences, and the Washington Research Foundation.
    Z.~Yan acknowledges support from the Max Planck Society and the Alexander von Humboldt Foundation in the framework of the Max Planck-Humboldt Research Award endowed by the German Federal Ministry of Education and Research.

    Author contributions are listed below: \\
    J.~F.~Crenshaw: created PZFlow, designed experiments, wrote paper. \\
    J.~B.~Kalmbach: wrote early normalizing flow code that evolved into PZFlow; photo-z estimation. \\
    A.~Gagliano: validated code, developed use cases and associated tutorials; revised manuscript text. \\
    Z.~Yan: contributed to PZFlow and PhotErr. \\
    A.~J.~Connolly: discussion during development. \\
    F.~Lanusse: wrote early normalizing flow code that evolved into PZFlow. \\
    A.~I.~Malz: consulted on design and testing of PZFlow. \\
    S.~J.~Schimdt: consulted on design and testing of PZFlow and PhotErr. \\
\end{acknowledgements}

>>>>

\author[0000-0001-5576-8189]{Andrew~J.~Connolly}
\affiliation{\dirac}

\author{Alex~I.~Malz}
\affiliation{\note{Alex's affiliation}}

@@

% this figure is so high just to move it ahead one page in the document
\begin{figure*}[t]
    \script{photo-z/plot_ensemble_posteriors.py}
    \begin{centering}
        \includegraphics{figures/ensemble_posteriors.pdf}
        \caption{
            The ensemble of posteriors for three example galaxies.
            Flows 1-4 label the individual posteriors produced by each of the flows that make up the ensemble.
            The dashed black line is the mean of these individual posteriors and is the value used by the ensemble.
            The vertical gray line labeled ``Truth'' denotes the true redshift of the galaxy.
            Note these galaxies were specifically chosen for their broad, multimodal posteriors.
            The posteriors of most galaxies are sharp and unimodal.
        }
        \label{fig:ensemble-posteriors}
    \end{centering}
\end{figure*}

@@

@@

\begin{acknowledgements}
    Thanks to François~Lanusse for some early advice on normalizing flows and for reviewing the paper.
    J.~F.~Crenshaw, B.~J.~Kalmbach, and A.~J.~Connolly acknowledge support from the DiRAC Institute in the Department of Astronomy at the University of Washington.
    The DIRAC Institute is supported through generous gifts from the Charles and Lisa Simonyi Fund for Arts and Sciences, and the Washington Research Foundation.
    Z.~Yan acknowledges support from the Max Planck Society and the Alexander von Humboldt Foundation in the framework of the Max Planck-Humboldt Research Award endowed by the German Federal Ministry of Education and Research.

    Author contributions are listed below: \\
    J.~F.~Crenshaw: created PZFlow, designed experiments, wrote paper. \\
    J.~B.~Kalmbach: wrote early normalizing flow code that evolved into PZFlow; photo-z estimation. \\
    A.~Gagliano: validated code, developed use cases and associated tutorials; revised manuscript text. \\
    Z.~Yan: contributed to PZFlow and PhotErr. \\
    A.~J.~Connolly: discussion during development. \\
    A.~I.~Malz: consulted on design and testing of PZFlow. \\
    S.~J.~Schimdt: consulted on design and testing of PZFlow and PhotErr. \\
\end{acknowledgements}
